---
title: "Introduction to StatComp21086"
author: "Li Xiangchao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp21086}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

__StatComp21086__  uses a new method to compute the rank CUSUM statistic, simply by calculating the depth of each sample point and then ranking them according to their values.

Here is a description of the functions of this package and how to use them

The simple principle of this package is as follows

$$\hat{k}^{*}=\min \left\{k:\left|Z_{N}(\lfloor k / N\rfloor)\right|=\sup _{0 \leq t \leq 1}\left|Z_{N}(t)\right|\right\}$$
$$ \hat{\theta}=\frac{\widehat{k}^{*}}{N}$$
$\hat{\theta}$ is the estimated relative location of change point.


## Compute depth of every point and rank them

The source R code for _data_depth_ is as follows:
```{r,eval=FALSE}
library(depth)
data_depth<-function(data,method){
  if(method==1){
    madist<-mahalanobis(data,colMeans(data),cov(data))
    madist
  }else{
    N<-nrow(data)
    nc<-ncol(data)
    dep<-numeric(N)
    meth=ifelse(nc<3,"Tukey","Oja")
    dep_comp<-function(y){
      depth::depth(y,data,method = meth)
    }
    apply(data, 1, dep_comp)
  }
}


```

This function contains two parameters, one for the data and one for the specified method,If method=1 is specified, then the depth is calculated using the mahalanobis function,otherwise use the oja function or tukey function.



The source R code for _depth_rank_ is as follows:
```{r,eval=FALSE}
depth_rank<-function(data,method){
  dep <- data_depth(data,method)
  rank(dep,ties.method = "first")
}

```

This function ranks the data according to each depth value


## Compute rank-CUSUM statistic

```{r,eval=FALSE}
Z.t<-function(data,method,t){
  N<-nrow(data)
  Nt<-N*t
  n<-floor(Nt)
  mean<-(N+1)/2
  sig<-sqrt((N^2-1)/12)
  r<-depth_rank(data,method)
  normalized_rank<-(r-mean)/sig
  trank<-normalized_rank[1:n]
  sum(trank)/sqrt(N)
}

```

The Z.t function calculates the statistic at some t, t between 0 and 1


```{r,eval=FALSE}
Z_stat<-function(data,method){
  N<-nrow(data)
  mean<-(N+1)/2
  sig<-sqrt((N^2-1)/12)
  r<-depth_rank(data,method)
  normalized_rank<-(r-mean)/sig
  cumsum(normalized_rank)/sqrt(N)
}

```
This function calculates the statistic at each sample point.

## Detect the change point.

```{r,eval=FALSE}
chan_poi<-function(data,method){
  Z<-Z_stat(data,method)
  M<-max(abs(Z))
  which(Z==M)
}

```

## An example for the package is given :

```{r,eval=FALSE}
set.seed(258)
library(StatComp21086)
library(mvtnorm)
mu1<-rep(1,20)
sig1<-diag(10,20)
sig2<-diag(c(9,8,7,rep(10,14),7,8,9))
mu2<-seq(from=0.55,to=1.5,by=.05)
x<-rmvnorm(100,mu1,sig2)
y<-rmvnorm(100,mu2,sig2)
data<-rbind(x,y)

z<-Z_stat(data,1)
plot(z,type="l",col='blue')
chan_poi(data,1,2)
```
The mahalanobis function is recommended due to the advantage of the speed of the calculation,especially in the case of large dimensions.

Under relatively mild conditons,the following equation holds:
$$
|\theta-\hat{\theta}|=o_{p}(1)
$$